### 2020-06-04 Documents/ChaoticDynamics/WriteUp.tex
Updated ESA and Write Up

\begin{figure}[h]

	\centering
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run1.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run2.png}
	\end{subfigure}

	\caption{$\alpha = 0.1$, $\gamma = 0.1$, $\tau \in [0.1, 10]$, $\Gamma \in [-1, 1]$. Each
	simulation is run for 1e5 iterations and tested for convergence. The game is said to have
	converged based on a tolerance of 1\% difference between action probabilities. For each
	combination of $\tau$, $\Gamma$ the game is played 5 times, each with random payoff matrices
	and initial conditions. The average number of converged games (giving an indication of
	probability of convergence) is shown in each cell of the heatmap.}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run1.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run2.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}
	%
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Alpha_2.png}
	\caption{$\alpha = 0.2$}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Alpha_2_Run_2.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}

	\caption{$\alpha = 0.1$, $\gamma = 0.1$, $\tau \in [0.1, 10]$, $\Gamma \in [-1, 1]$. Each
	simulation is run for 1e5 iterations and tested for convergence. The game is said to have
	converged based on a tolerance of 1\% difference between action probabilities. For each
	combination of $\tau$, $\Gamma$ the game is played 5 times, each with random payoff matrices
	and initial conditions. The average number of converged games (giving an indication of
	probability of convergence) is shown in each cell of the heatmap. \label{fig::Toys}}
\end{figure}

To generate the numerical simulations in Figure \ref{fig::Toys} we used the following procedure.

\begin{enumerate}
	\item Fix the parameters $\alpha$ and $\gamma$. The latter is held fixed at $0.1$ since
	it does not affect the long term behaviour of the system (it does not appear in (
	\ref{eqn::EOM})).
	\item We initialise values of $\Gamma$ and $\tau$. These will be the variables which we sweep
	over.
	\item Generate payoff matrices for both agents by sampling from a multi-variate Gaussian 
	(variables are the payoff elements) with covariance parameterised by $\Gamma$.
	\item Iniitialise the agents with random initial conditions (i.e. random action probabilities).
	\item Allow the agents to learn over a maximum of $1 \times 10^5$ iterations.
	\item Every 100 iterations, check to see if the action probabilities have changed significantly.
	If not (i.e. the change over the last 100 iterations is less than 1\%) the learning is
	considered to have converged.
	\item This process is repeated 5 times with random payoff matrices generated based on the value
	of $\Gamma$. The probability of convergence is then recorded as $\frac{\text{number of times
	converged}}{5}$.
	\item The values of $\tau$ and $\Gamma$ are then modified and the process is repeated. The
	heatmap shows the probability of convergence for all values of $\tau$ and $\Gamma$ which are
	tested.
\end{enumerate}

### 2020-06-04 Documents/ESA/sections/LitReview.tex
Updated ESA and Write Up

@@

    \section{Game Theory} \label{sec::Game_Theory}
    \subsection{Stochatic Games} \label{sec::Stochastic_Games}
    \subsection{Game Theoretic Control} \label{Game Theoretic Control}

    \section{Multi Agent Reinforcement Learning} \label{sec::MARL}
    \subsection{Learning in Two Player Games} \label{sec::Two_Player_Games}
    \subsection{Learning in Stochastic Games} \label{sec::Learning_Stochastic_Games}
    \subsection{Multi Agent Learning Dynamics} \label{sec::MARL_Dynamics}

    \section{Control Theory} \label{sec::Control_Theory}
    \subsection{Distributed Model Preodictive Control} \label{sec::Distributed_MPC}
    \subsection{Approaches to Swarm Control} \label{sec::Swarm Control}

    \section{Swarms} \label{sec::Swarms}
    \subsection{Decision Making in Swarms} \label{sec::Decisions_in_Swarms}

>>>>

In this chapter, we explore the current state of the art in Multi-Agent Systems (MAS). We will
consider the main techniques that have been proposed towards task allocation and control.

@@

\textbf{TODO: Elaborate on each of the metrics}

We will keep the problem statement defined in Section \ref{sec::Objectives_and_Scope} in mind as
we define several metrics which a Multi Agent System (MAS) may be assessed against.

\begin{enumerate}
    \item Scalable
    \item Distributed
    \item Generality
    \item Low Computational Load
    \item Robustness
\end{enumerate}

We will use these metrics, alongside the problem statement to approach the current literature
surrounding the theory and practices of Multi-Agent Systems.

\section{Game Theory} \label{sec::Game_Theory}

Game Theory has a rich history when considering an understanding of multi-agent systems and it
is impossible to examine MAS without an understanding of Game Theory. These
begin in economics but have found a strong application in computation due to the rising need for
distributed systems. Game Theory, therefore, branches across all of the categories in this
chapter although its synergy with swarms requires development) since Dec-POMDP
and MARL methods have both base their theory upon the foundations of Game Theory.

\subsection{Partially Observed Stochatic Games (POSG)} \label{sec::Stochastic_Games}

POSGs act as a game theoretic corollary to the Dec-POMDP. Here, an optimal solution is found by fixing the strategy (a manner of selecting an action \cite{Rizk2018DecisionSurvey}) of all agents except one. The optimal strategy of the chosen agent is then computed. This is fixed so that the next agent may determine its optimal strategy. This process is iterated over all agents in a process known as Alternating Maximisation \cite{Ray2010AnCooperation}. By choosing strategies which maximise a common payoff, a globally optimal solution can be found.

Similarly Bayesian Games is a game theoretic approach with incomplete information (thus it is sometimes referred to as an ‘incomplete information game’). This allows for a POSG to be approximated by a sequence of smaller, more tractable games \cite{Emery-MontemerloApproximatePayoffs}. However, iterating through the entire team of agents to find an optimal solution is a lengthy process and does not allow for immediate actions in dynamic situations. To address this, \cite{Ray2010AnCooperation} propose to place distinct payoffs on each agent and to consider team formation based on social hierarchy as well as preferred partners. This allows the complexity of the problem to be broken down into smaller game units and also provides a clear order in which the games are to be played. This minimises the interference across robots and allows for more immediate action to be taken by agents who choose their strategy early on, while leaving more passive tasks for those later in the sequence.

The Bayesian Game formulation therefore provides a strong candidate for rapid task re-allocation and dynamic decision making. However, as found by Dai et. al \cite{Dai2018TaskSystems} this is conditional on an understanding by each robot of the strategy of others, which in turn requires adequate communication between robots. Therefore, the game theoretical formulation will fail where communication is not possible amongst team members. However, the addition of heuristics, such as deep learning, may be able to advance an agent’s ability to recognise the strategies taken by other members of its team without the need for significant explicit communication.

\textbf{Add in any recent literature in these fields}

\subsection{Game Theoretic Control} \label{Game Theoretic Control}

Game theory can often be applied to problems of control theory (particularly where there are
multiple agents) to develop robust controllers which guarantee properties of stability and
constraint satisfaction.

This idea is explored in \cite{Marden2018AnnualControl}. Here, a zero-sum game is considered in
which the players are a controller and an adversarial environment. The design of the controller must
be such that it is able to drive the system to zero error. To illustrate, consider the problem of
designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which
vortices seek to destabilise the agent. This will allow us to build stable agents in a much more
efficient manner since we can simulate the adversarial environment and hypothetical scenarios the
agent may encounter without actually encountering them. The same notion is explored by Bardi et al
\cite{Bardi1991DifferentialDisturbances}.

Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
avoidance problem, similarly from the point of view of differential game theory. They develop a
robust feedback system for the robots which they show to be able to drive the system towards
predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
systems in a distributed manner. Here, agents only consider their own payoff structure and have
limited communication with one another. The author shows that an approximate equilibrium can be
found using algebraic methods and illustrate the capabilities of the technique using a collision
avoidance example. For the sake of brevity the numerous contributions that Mylvaganam has made to
this field is not presented here. However, we will conclude with those presented in
\cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
games, including linear-quadratic differential games (in which system dynamics are linear functions
whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is 
induced across the players (a notion was suggested in the research proposal) and mean-field games,
which is discussed in 'MARL'. The importance of the linear-quadratic
differential game is the stability of the solution; solutions for the Nash equilibria (NE) are
admissable iff they are locally exponentially stable (which the author often shows with the aid of
Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
calculate online. The author then shows that this is not simply a theoretical exercise by applying
the novel methods towards multi-agent collision problems and designs dynamic control laws which
guarantee that each agent will reach their desired state whilst avoiding collision with the other
agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
robot system.

\section{Multi Agent Reinforcement Learning} \label{sec::MARL}

Reinforcement learning extends the Markov Decision Process problem by considering the case where the
reward model is not initially known to the agent. In a similar manner, Multi Agent Reinforcement
Learning (MARL) extends the Markov Game setting to one where the payoff structure is not a priori
knowledge.

The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
policy may be the concatenation of all the individual policy or it may just be options for each
agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
and so, in this section, I will try to consider the broad spectrum of methods which attempt to
achieve this Nash equilibria. The largest problem in MARL is the non-stationarity of the environment
\cite{Hernandez-LealA}. In single-agent settings, it is assumed that the environment is Markovian.
However, this must be lifted in the Multi Agent setting since other agents in the environment will
be learning concurrently. As such, we must now consider that the policy for any one agent will
depend on the policy of all other agents.

This chapter begins with a selection of the foundational methods which were developed towards
solving the MARL problem. The interested reader may find additional methods and implementations of
these techniques in \cite{SchwartzMulti-agentApproach}.

\subsection{Learning in Two Player Games} \label{sec::Two_Player_Games}

The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
method of linear programming (in which constraints are linear). This will be important in
considering more current methods. A similar consideration is given to the infinitesimal gradient
ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
particular problem in games where there are multiple Nash equilibria. However, in practice it is
difficult to choose a convergence rate of the step size and, without an appropriate choice the
strategy may oscillate as shown in the book. To address this, a modified approach is presented by
Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
payoff matrix (which is not so much of a problem for model based methods) and the opponent's
strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
players with minimal oscillation.

\subsection{Learning in Stochastic Games} \label{sec::Learning_Stochastic_Games}

Stochastic Games (or Markov Games) form a basis for MARL settings. However, in this case the agents
must learn about the equilibrium strategies by playing the game, which means they do not have a
priori knowledge of the reward or transition functions. Schwarz considers two properties which
should be used for evaluating MARL algorithm: rationality and convergence. The latter simply states
that the method should converge to some equilibrium whereas the former suggests that the method
should learn the best response to stationary opponents. A similar set of conditions is considered by
Conitzer and Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider shortly. Schwarz
then presents a review of MARL methods (as of September 2014)

\textbf{Add in more recent literature r.e. learning in stochastic games}

\subsection{Multi Agent Learning Dynamics} \label{sec::MARL_Dynamics}

Multi Agent Learning Dynamics (often referred to as Game Dynamics or Learning Dynamics)
considers the
problem of mathematically modelling Multi Agent Systems who adapt through repeated interact with one
another. This model then serves to be able to predict the evolution of the system as well as to
understand the trajectory of learning. Typically, this looks at considering whether or not the
method is likely to converge towards a Nash equilibrium. This is generally a difficult problem to
solve \cite{ShohamMultiagentFoundations} for all but toy problems.
\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
Stability provides some guarantees against the stochastic nature of the environment since a stable
equilibrium will always be returned to even after perturbations. This extremely important in Safe
and Trusted AI as it provides guarantees against undesired behaviour in real world environments.

The area of dynamics which has shown most promise in Multi-Agent Reinforcement Learning is that of
evolutionary dynamics. This draws from the principles of Evolutionary Game Theory (EGT) which
considers similar assumptions to that of MARL: agents are no longer required to be rational and
play the game optimise their expected return through repeated play. Importantly, players have no
knowledge of the others' payoffs \cite{Tuyls2006AnGames}. In \cite{Tuyls2006AnGames}, Tuyls et al.
determine the relation between the replicator dynamics concept of EGT (a differential equation
defining the evolution of the proportion of a subgroup in an evolving population) and Q-Learning
using Boltzmann probabilities as Q-values. The result was a dynamics equation which describes, for
each action, the evolution of its selection probability which could even account for random
exploration. There have since been a number of works which apply the same insight into different
game types and MARL algorithms. In \cite{Bloembergen2015}, these are broken into the following
categories

\begin{itemize}
    \item Stateless games with discrete actions. Here, stateless refers to the idea that the game is
    static and so the environment has no impact on the result. The aforementioned result 
    \cite{Tuyls2006AnGames} fits into this category.
    \item Stateless games with continuous actions. These consider more realistic MARL than the
    previous category by replacing each agent's strategy vector with a probability density function 
    (pdf) over a continuous action space.
    \item Stateful games with discrete actions. This mostly considers stochastic games, where there
    are multiple states with probabilistic (usually Markovian) transitions between them. However,
    extensive form games, which considers more complex phenomena such as sequential moves and
    imperfect information, are also briefly mentioned.
    \item Stateful games with continuous actions. This is one of the more realistic assumptions
    considered. However, the authors point out that this area is yet to see results, leaving it open
    for possible research.
\end{itemize}

Though the above have seen success through experimental validation in games with 2 players and (in
general) 2 to 3 discrete actions, recent work has begun the consideration of improving the models
towards more complex scenarios with larger agent populations. A recent example of this is 
\cite{Hu2019}, in which Hu uses a mean field approximation to model the dynamics of a population of
Q-Learning agents. As a reminder, mean field (MF) approaches in MARL consider that an agent updates
its strategy based on the mean effect of the population. The result is a system of three equations
which describes the evolution of Q-values over a large population in a symmetric bi-matrix game.This
presents an important first step in modelling the learning dynamics of large agent populations and
has the scope to be expanded to systems of asymmetric games, heterogeneous populations and stateful
games.

An advantage of determining the evolutionary dynamics of learning is that it can describe the
expected behaviour in different game settings. This is particularly important to understand the
convergence of the methods; certain games will often show cyclic behaviour even with the existence
of a strict NE. For instance, Imhof et al. show in \cite{Imhof2005} that a repeated prisoner's
dilemma game results in cyclic behaviour when considering the options of cooperation or defection.

\section{Control Theory} \label{sec::Control_Theory}

The control theoretic perspective considers generating a set of control laws for the system. These
are chosen with the aim to satisfy certain properties. The main properties are

\begin{itemize}
    \item Stability, that a system will return to the desired setpoint (or within a neighbourhood) if
    perturbed.

    \item Robustness, that a system will perform its function in the presence of uncertainty and
    noise

    \item Optimality, that the system will achieve some defined function

    \item Feasibility, that the controller will always be able to generate a control law which
    satisfies the desired properties.
\end{itemize}

There are a number of approaches towards control systems. However, the interest of this review lies
in multi-agent systems which must operate in the face of uncertainty. As such, we focus on
stochastic and distributed control. The literature of the control communnity is vast and can be
divided into a number of sub-fields. We consider Distributed MPC (DMPC) and Swarm Optimal Control as
those which are particularly relevant to this study and review them in this section.

\subsection{Distributed Model Preodictive Control} \label{sec::Distributed_MPC}

Rawlings et al \cite{rawlings2017model} divide the problem of distributed control into four distinct
categories: decentralised control, non-cooperative control, cooperative control, and centralised
control. The last of these is not considered in the text since it only considers the case in which a
centralised controller has access and can manipulate multiple agents at once.

Decentralised control is the scheme in which agents do not have information about the actions of
other agents and can only optimise for their own objective. This has the advantage of requiring no
communication, but can often lead to poor performance when the agents are strongly coupled as each
agent’s model is incomplete. In the non-cooperative setting, each agent optimises their own loss
function whilst treating the others’ actions as a known disturbance. In this setting, each agent has
knowledge of the others’ control laws and their effect. In this case, the agents must communicate
their intended actions to one another and iterate to achieve a consensus (or Nash equilibrium). This
is the same for cooperative control, except that the loss function is now shared across the team.

Of all of these systems, cooperative control has found greatest applicability in autonomous systems
\cite{Negenborn2014}, perhaps due to the favourable stability properties \cite{Venkat2006}. One
particularly strong application of this system is in vehicle platooning. Here, self-driving cars or
unmanned aerial vehicles (UAVs) must move in a certain formation without colliding into one another.
A number of examples can be found such as in \cite{Liu2019, VanParys2017, Zheng2017}. Distributed
MPC provides the advantage that guarantees can be placed regarding coupled constraint satisfaction
and feasibility.

The advances in stochastic and robust MPC, however, do lend themselves towards revisiting the
capabilities of decentralised control. Recall that, in this scheme, the agents cannot communicate
with one another. However, advances in MARL show us that this disadvantage can be made less
prevalent if each agent has a model of the other \cite{Foerster}. To this end, a methodology such as
presented in \cite{Heirung2019} may prove beneficial in the decentralised scheme. Here, the system
chooses amongst a family of system models when choosing its control laws. Similarly, agents who
determine (or perhaps learn) models of the other agents may be able to leverage this information,
minimising the model error when optimising.

\subsection{Approaches to Swarm Control} \label{sec::Swarm Control}

Recent work has seen the advancement of swarms controlled in stochastic environments. This is
particularly important for swarm intelligence in robots; many systems are developed with the
motivation of search-and-rescue, in which the robot swarms will have to operate in environments
where accounting for uncertainty is critical. To this end, swarm systems have seen the advent of
stochastic control. In this, the swarm is modelled as a diffusive system using a stochastic
equation, most often the Kolmogorov Forward Equation \cite{Hamann2008}. In \cite{Hamann2008}, the author shows that this equation can be derived by considering local trajectories of
smaller subsets of the swarm. Elamvazhuthi and Berman \cite{Elamvazhuthi2019} extend this idea to other
stochastic models for swarms, importantly considering an advection-diffusion-reaction model which
allows for hybrid agents to switch between different modes of operation.

The above models come under the term ‘mean-field models’ \cite{Elamvazhuthi2019b}, a series of
equations
for stochastic forward processes (such as swarm foraging) in which, as the number of agents tends to
infinity, the true macroscopic motion of the system tends to these equations. Importantly, however,
these stochastic equations allow for an analysis of the swarm, as well as the ability to develop
control laws. In \cite{Li2017}, Li et al show that these models can be used to develop control
laws for robots in a swarm and drive them towards a target distribution. The method is shown to
perform accurately both in simulation and on real robots. The advantage is that guarantees can be
placed on the convergence and stabilisabiilty of the swarm towards the desired distribution.
However, there appears to be significant scope to expand upon this methodology from a safety
perspective. To begin with, the method does not consider inter-agent interactions and therefore does
not formally guard against collisions. In \cite{Inoue2019}, a similar problem is considered,
although collisions are avoided by having the robot simply move in the opposite direction when
encountering an obstacle. It is here that the mean-field models are not as strong since they do not
take these local interactions into account. It must be noted, however, that Inoue et al have
identified this problem and are currently working towards its incorporation into the model.

It would, therefore, be of particular interest from a safety perspective to consider agent
interactions. A starting point may be \cite{Bellomo2017} which extends the dynamical model of a
swarm system to include agent interaction. This presents a first step towards considering the swarm
as composed of intelligent agents rather than mindless particles and, as the authors suggest,
presents the possibility of applying game theoretic approaches towards swarms, which also gives the
ability to consider heterogeneous swarm systems who interact with one another through repeated play.
Similarly, it would allow for a stronger control perspective on swarm systems such as presented in
\cite{Borzi2015}, in which a model predictive control (MPC) scheme is presented for a
leader-follower swarm system to achieve given tasks.

\textbf{Include recent updates in here}

\section{Swarms} \label{sec::Swarms}

Swarm systems comprise of a population of (typically) homogeneous agents who are able to organise
themselves
into formations using a series of simple local interactions with their neighbours
\cite{Couceiro2015}. Whilst the individual agents are generally simplistic, the collective behaviour
may exhibit complex phenomena emulating systems observed in biological organisations such as bee or
ant colonies \cite{Sethi2017}. Hybrid algorithms such as in \cite{Gao2018} show an accelerated
performance in reaching globally optimal solutions in search-based tasks. The advantage of many
swarm algorithms is that they are based on local interactions and so are incredibly scalable
\cite{Rizk2018}.

\subsection{Decision Making in Swarms} \label{sec::Decisions_in_Swarms}

\textbf{Include Marco Dorigo and Recent AAMAS literature in here}

The reduction of the complexity in interactions between agents also allows for the robots to perform
other calculations on board. In \cite{Pini2011TaskSelection}, Pini et al. leverage this by
considering adaptive task partitioning across swarms. This allows a swarm, in a decentralised
manner, to deliberate whether to partition a task into its sub-tasks or to perform the task in its
whole. As of now (to the best of my knowledge) the problem of partitioning general tasks into its N
sub-tasks is unexplored. This, however, highlights another advantage of swarm systems; they are
readily divided into sub-groups (as in \cite{Zahadat2016DivisionInhibition}) to perform a
divide-et-impera (divide and conquer) approach to solving problems \cite{Pini2011TaskSelection}).

Furthermore, swarm systems may be designed in a leaderless manner and so do not require the use of a
central controller \cite{Couceiro2015}. This presents the advantage that the system can rapidly
adapt to the loss of agents or separation of groups throughout the task. However, the assumptions
made regarding the homogeneity of individual agents and the simplicity of their local interactions
result in significant limitations placed on the complexity of the tasks that swarm systems can
accomplish.

\section{Remarks} \label{sec:remarks}

\textbf{TODO: Go through each of the sections and explicitly evaluate them against the defined
metrics}

### 2020-06-04 Documents/ESA/sections/ProposedResearch.tex
Updated ESA and Write Up

\begin{document}
    \section{Chaotic Dynamics in MARL} \label{sec::Chaos_in_MARL}
    \section{Large Agent Dynamics} \label{sec::Large_Agent_Dynamics}
    \section{Swarm Control through Fields} \label{sec::Swarm_Field_Control}
    \section{Incorporation of Intelligence in Control} \label{sec::Intelligence_in_control}
\end{document}

>>>>

\begin{document}

	\textbf{Major restructuring and rephrasing is required here}

    \section{Chaotic Dynamics in MARL} \label{sec::Chaos_in_MARL}
    The intention of this area of study is to consider the ideas presented in works such as 
    \cite{Sanders2018} and \cite{Galla2011} which consider complex behaviour, including cycles and
    chaos, in certain games using simple reinforcement learning algorithms. These provide a great
    deal of insight into whether or not the game will converge and, if so, to what equilibrium.
    Galla, for instance, shows that adjusting a memory parameter when learning to solve an Iterated
    Prisoner's Dilemma game can shift the equilibrium from one showing purely defective behaviour to
    one showing cycles of cooperations and defection. Sanders et al. generalise this result by
    showing that, for a particular learning algorithm known as Experience Weighted Attraction,
    learning dynamics varies dependent on the mutual effect of two parameters.

    This determination of where RL algorithms will show complex dynamics is important, not only for
    a priori understanding of resultant behaviour, but is particularly important for algorithms in
    which agents aim to predict the behaviour of other agents. For this to be feasible, the learning
    dynamics must not exhibit chaos, otherwise it would be impossible for an agent to make any
    reasonable predictions about the future behaviour of its opponents.

    To this end, the potential avenue for research in this regard is to extend the ideas of Sanders
    et al. and Galla et al. towards games learnt using classical reinforcement learning algorithms 
    (such as Q-Learning with Boltzmann exploration, which seems to be a common choice). The work may
    then be able to extend beyond this, and towards continuous spaces, stateful games and large
    agent populations. This would allow for an understanding of the important parameters which
    define the behaviour of reinforcement learning algorithms and allow for a characterisation of
    the expected resultant behaviour when applying a particular algorithm to a particular game. It
    would also allow for a characterisation of the conditions under which MARL algorithms may
    feasibly be applied, thereby supporting the ability of researchers and engineers to choose their
    payoff matrices and parameters accordingly.
    \section{Large Agent Dynamics} \label{sec::Large_Agent_Dynamics}
    This suggestion aims to build upon the work presented by Leung et
    al. \cite{Hu2019} in which the point is made that the vast
    majority of the work done in this area considers games with a
    finite (usually two) number of agents. This limits the capability
    of the analysis to generalise to much larger agent populations,
    such as swarms. To allieviate this concern, the authors present an
    anaysis of the learning dynamics for a large agent population
    (which they approximate as containing infinite agents) where each
    agent is an independent Q-Learning using Boltzmann
    exploration. The emergent dynamics is given by a Fokker-Planck
    equation which is numerical shown to be a strong approximation of
    the true learning dynamics. However, as the authors point out,
    this is the first attempt at considering such a problem, and
    relies on heavy assumptions.  Possible extensions therefore
    require a consideration of:

    \begin{itemize}
        \item Asymmetric games, in which agents have different
          payoffs, introducing heterogeneity and competition into the
          system. \fr{this is not really a problem  in relation with swarms, is it?}
        \item Stateful Games. \fr{what is the interest of stateful games?}
        \item Heterogeneous populations, in which there are p different populations of agents.
    \end{itemize}

    To the best of my knowledge, in the particular case of $N >> 1$ agent populations, none of the
    above have yet been attempted.

    \section{Swarm Control through Fields} \label{sec::Swarm_Field_Control}
    This study extends the work of Zhang \cite{Zhang2018}, Elamvazuthi \cite{Elamvazhuthi2019} and
	Li et al. \cite{Li2017}. Here, the authors consider the dynamics of swarms through 'drifted
	brownian motion'. In this case, the control input is some scalar field which is generated from the
	environment. Each agent measures this field at their location and uses it to adjust their
	velocity, which eventually results in the entire swarm achieving a desired distribution. This technique
	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
	manner.

	The hypothesis of this section is that the distribution of active particles may
	similarly be controlled through the influence of a scalar field. The dynamics derived by Bellomo
	et al. \cite{Bellomo2017} includes a 'flocking field' which agents can measure. By controlling
	the flocking field, we may be able to drive the swarm to specific
	distributions.

	The contribution that this study presents over those using brownian motion is the inclusion of an
	interaction operator. This governs how agents interact with one another. By accounting for this, we
	are able to control swarms where agents, for instance, avoid collisions with one another. The
	complexity of this interaction term will need to be gradually increased over time. To begin with,
	we may entirely neglect this term. It is here that we will compare the model proposed by Zhang with
	that proposed by Bellomo et al. We may then consider only local interactions, which is typical for
	most swarming systems in the current literature, before then considering non-local interactions.
	This provides the scope for swarms to interact with a greater number of agents. At this
	stage, we may expand our study to consider the presence of interaction domains. This places
	constraints on how agents may interact with one another, allowing for a greater generalisation of
	inter-agent interactions. Ultimately, we would like to influence the interaction term, though this
	is discussed in Section \ref{sec:learning_strategies_through_iterated_interaction}. The questions
	we will consider here are:

	\begin{itemize}
		\item The controllability of the system: Under what conditions is it possible to drive the
		swarm from one configuration to another in a stable manner?
		\item The guarantees of the system: Is it possible to ensure that the agents will not enter
		certain areas of state space, or exceed certain control constraints (e.g. max imum velocity)?
	\end{itemize}

	Some applications of this study are:

	\begin{itemize}
		\item Search and Rescue, in which agents will be required to flock to specific areas (e.g.
		areas with survivors detected).
		\item Construction, in which agents will be required to take on desired formations based on
		the structure to be designed.
		\item Medical Robotics, in which agents are required to target specific areas of the body.
	\end{itemize}

	In conclusion, the results from this study already significantly expand the current capabilities of
	swarming agents by developing control methodologies which can drive the swarm towards desired
	distributions in a stable manner. This is accomplished through controlling the 'flocking field'
	which is indirectly used to adjust the velocity of the agents.

    \section{Incorporation of Intelligence in Control} \label{sec::Intelligence_in_control}

    This section of the study is perhaps the strongest extension to swarm control proposed in this
	chapter, and will likely be the most challenging. Here, we attempt to control the interaction term
	in Bellomo et al's model and we consider that the behaviour of the entire swarm may be influenced
	by decision making on an individual level. This will involve agents learning their strategies
	through repeated interaction. The goal, then, is to design the agent parameters, reward structure
	and control strategy to achieve desired results. To accomplish this will require a unification of
	multi agent learning and control theory. Whilst, at first glance, such an endeavour seems
	incredibly challenging, our work in the predictability of mean field learning (Chapter 
	\ref{ch::DynMARL}) places us in a unique position to tackle the problem. This framework will
	first establish the desired strategy to be taken by the agents and choose the game's reward
	structure so that learning will converge to a stable fixed point. Then by accounting for this
	strategy within the interaction term, we apply the appropriate controls in the flocking field to
	drive the swarm in a stable manner. We will again consider the aforementioned controllability
	and guarantees questions and establish how the incorporation of learning affects these results.

\end{document}

### 2020-06-04 Documents/Literature Review/Literature Review - Revised/sections/SwarmControl.tex
Updated ESA and Write Up

	\begin{itemize}
		\item Measurements of physical properties, such as the intensity of light or heat 
		(particularly useful when aiming to avoid fires in urban search and rescue), or
		concentration of pollutants for enviromental applications.
		\item Density of the environment through computer vision. For instance, a centralised sytem may map the environment and artificially generate a field which it then communicates to the swarm.
		\item Shape detection for moving objects. For instance, picking up beams and bringing
		them to desired locations may be solved by appropriately choosing an underlying field.
	\end{itemize}

>>>>

	\begin{itemize}
		\item Measurements of physical properties, such as the intensity of light or heat 
		(particularly useful when aiming to avoid fires in urban search and rescue), or
		concentration of pollutants for environmental applications.
		\item Density of the environment through computer vision. For instance, a centralised sytem may map the environment and artificially generate a field which it then communicates to the swarm.
		\item Shape detection for moving objects. For instance, picking up beams and bringing
		them to desired locations may be solved by appropriately choosing an underlying field.
	\end{itemize}
